Data Preparation

### 2019-01-10 Data Preparation.Rmd

### Course Manual

From `manuals_td` we are only interested in the text, and the Code of the course. However, we don't have the code but we have a document id that includes it. Therefore we select only the `text` and `id` columns of the `manuals_td`. Then, we extract the code from the `id` and save it in under `Code`, We aso extract the concentration from the `id` and save it under `Concentration`. Finally, we unnest the dataframe to have only one word per row, and call this `manuals_tokens`, this creates a variable `word` and adds all of the text from the course manuals under this column.

```{r d_manual tidy}

####(Optional) Pre-processing Course Manuals- Removing stopwords
Some characters appear with sufficient frequency to be relevant but not often enough accross all courses to be deleted when using tf-idf (see sections bellow), it is therefore convenient to add some stopwords and remove numbers. For this we import stop_words from tidytext, and search all our words with grep for stand alone numbers. We save these words in different dataframes and then exclude with an antijoin.
```{r}

##Student Data

>>>>

##Student Data
(In this section we use: `d_transcript`- contains the transcript information of students as was provided. It has 40 columns, and rows correspond roughly to a type of grade (e.g. final grade, attendance) per student per course per time they took it).
